Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-21 chapters/final_remarks.tex
refined future work section
Changed I to we in results chapters

In Aim 3, I investigated the rheology of bijels stabilized by ellipsoidal particles under shear, examining the effects of initial microstructure and a 
constant magnetic field on their shear response. Using a Herschel-Bulkley fitting, I found that while shear-thinning behavior remains robust, the 
flow index and yield stress are strongly influenced by particle morphology and magnetic field application. Increased particle ordering led to 
lower yield stress in oblate-particle-stabilized bijels and higher yield stress in prolate-particle-stabilized bijels, highlighting the role of particle 
shape in interfacial mechanics. Without a magnetic field, both particle monolayers remained adsorbed at the interface, but when a field was applied, 
oblate particles flipped out of the interface, whereas prolate particles tilted, altering the flow field and impacting non-Newtonian behavior. Additionally, 
coarsening driven by reduced interfacial particle coverage emerged as the dominant mechanism behind domain size evolution in sheared bijels. The anisotropic 
domain growth trends matched expectations in all cases except when the field was removed, indicating that the history of field application significantly influences 
microstructural evolution. These findings provide insight into the interplay between particle morphology, interfacial coverage, and external fields, contributing 
to the understanding of magnetically tunable soft materials and structured emulsions.

@@

This work utilized 2 ellipsoidal particle geometries chosen for comparisons to previous literature using this 
particle geometry. Particles based on cellulose nanocrystals or graphene nanoplates are now in use to fabricate
particle stabilized emulsions. These particles have also been shown to have capillary bridging and particle stacking,
not seen in the particles used in this work. These particles in bulk have been shown to have some intrinsic ordering
that can be predicted using onsager theory. An investigation into how using rods or plate like particles would be 
instructive in identifying if onsager theory can be used in bijel formation and its link to bijel microstructure. 
\cite{tan_2d_2021}

>>>>

In Aim 3, the rheology of bijels stabilized by ellipsoidal particles under shear was analyzed, specifically examining the effects of initial microstructure and a 
constant magnetic field on the shear response. Using a Herschel-Bulkley fitting, shear-thinning behavior remains robust although the 
flow index and yield stress are strongly influenced by particle morphology and magnetic field application. Increased particle ordering led to 
lower yield stress in oblate-particle-stabilized bijels and higher yield stress in prolate-particle-stabilized bijels, highlighting the role of particle 
shape in interfacial mechanics. Without a magnetic field, both particle monolayers remained adsorbed at the interface, but when a field was applied, 
oblate particles flipped out of the interface, whereas prolate particles tilted, altering the flow field and impacting non-Newtonian behavior. Additionally, 
coarsening driven by reduced interfacial particle coverage emerged as the dominant mechanism behind domain size evolution in sheared bijels. The anisotropic 
domain growth trends matched expectations in all cases except when the field was removed, indicating that the history of field application significantly influences 
microstructural evolution. These findings provide insight into the interplay between particle morphology, interfacial coverage, and external fields, contributing 
to the understanding of magnetically tunable soft materials and structured emulsions.

@@

This work utilized 2 ellipsoidal particle geometries chosen for comparisons to previous literature using this 
particle geometry. Particles based on cellulose nanocrystals or graphene nanoplates are now in use to fabricate
particle stabilized emulsions. These particles have also been shown to have capillary bridging and particle stacking,
not seen in the particles used in this work. These particles in bulk have been shown to have intrinsic ordering
that can be predicted using onsager theory. An investigation into how using rods or plate like particles would be 
instructive in identifying if onsager theory can be used in bijel formation and its link to bijel microstructure. 
\cite{tan_2d_2021}
